Title

### 2017-03-19 paper.tex
Change Title of section 3 and 4
Draft of section 4 and reference
Updated tex source to use IEEEtrans format template

\documentclass[10pt,a4paper]{article}
\usepackage[english]{babel}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{url,hyperref,graphicx,float,times}
\usepackage{sectsty}
\usepackage{authblk}
\usepackage{textcomp}
\renewcommand{\refname}{}

\setlength{\paperheight}{297mm}
\setlength{\paperwidth}{210mm}
\setlength{\voffset}{-12mm}
\setlength{\topmargin}{0mm}
\setlength{\headsep}{8mm}
\setlength{\headheight}{10mm}
\setlength{\textheight}{235mm}
\setlength{\hoffset}{-4mm}
\setlength{\textwidth}{166mm}
\setlength{\oddsidemargin}{0mm}
\setlength{\evensidemargin}{0mm}
\setlength{\marginparwidth}{0mm}
\setlength{\marginparpush}{0mm}
\setlength{\columnsep}{6mm}
\setlength{\parindent}{6mm}
\setlength{\parskip}{2mm}

%% insert table
%% use as \tabin{size_in_mm}{label}{caption}{table_data}
\newcounter{tabcounter}
\def\tabin #1#2#3#4{
\refstepcounter{tabcounter} \label{#2}
\[ \makebox[#1][c]{#4} \]
%\vspace{0mm}
\begin{center}
  \parbox{7cm}{{\bf Table \arabic{tabcounter}:}\quad {\it #3 } } \\
\end{center}
}

\title{\LARGE
Title
}

\author[*]{\large
{\bf Ching-Chun (Jim) Huang}\thanks{jserv@ccns.ncku.edu.tw}}
\author[**]{\large
{\bf Chung-Fan Yang}\thanks{E24026048@mail.ncku.edu.tw}}
\affil[*]{Department of Computer Science and Information Engineering,
\newline
National Cheng Kung University, Taiwan
\newline
No.1, University Road, Tainan City 701, Taiwan (R.O.C.)}
\affil[**]{Department of Electrical and Electronic Engineering,
\newline
National Cheng Kung University, Taiwan
\newline
No.1, University Road, Tainan City 701, Taiwan (R.O.C.)}
\date{}

@@

@@

\vspace{10mm}

\begin{multicols}{2}

@@

\section{Methodology Environment}

    Based on the works presented above, we had found out several problems in common methodology method used currently.
    First, the methodology tool, e.g. cyclictest, is over-simplified. It only gives the wakeup latency measurements,
    which sometimes is not the main or only performance bottle-neck of a real-time system. Also, general profiling
    tools, e.g. perf, is typically utilizing the sampling methodology method, lacking high fidelity, all-recorded
    profiling result of the target system in microsecond scale, which is usually seen in real-time system tuning. In
    addition, the behavior and loading characteristic of work-load used during test, e.g. hackbench, stress, etc. are
    far from the real target applications. These problems not only would significantly reduce the effectiveness of
    tuning target system, but also will cause actual hazards, harming the real-time performance, obscure.

    Our approach to counter these problems includes a new profiling method and a test work-load, which is able to
    represent the target real-time application. The new profiling tool is derived from paper A Decade of Wasted Cores,
    published in EuroSys 2016. In A decade of Wasted Cores, authors have development a profiler which instruments the
    scheduler of Linux Kernel, extracting scheduling information. Based on this work we have extended the ability of the
    profiler to extract the running entity of each core of the target system also the context-switching information,
    including time and target process id (PID). This enabled us to record and collect kernel scheduling information,
    running PID of each processor core fully during the execution of work-load. The recorded data resolution is based on
    the timer resolution of kernel scheduler. On x86-64 and ARM platform, the resolution could achieve sub-microsecond
    level. This gives us the advantage to justify when would the processor core executes the real-time task, how
    work-loads were scheduled by the kernel scheduler, and random scheduling events. This level of detail could not be
    achieved with the previous mentioned tools, which only utilizes the processor's performance measurement unit (PMU),
    lacking the fidelity requires during the tuning of real-time system.

@@

    In aid of these developed tools and work presented above, we proposed a high accuracy methodology system, and apply
    this on various platform, including x86-64 and ARM.

\section{Methodology Result}

\bibliographystyle{unsrt}
\begin{thebibliography}{9}%use this if you have <=9 bib refs
	\bibitem {rtai}{\it https://www.rtai.org/}
\end{thebibliography}

\end{multicols}
\end{document}

>>>>

\documentclass[conference]{IEEEtran}
\usepackage[english]{babel}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{url,hyperref,graphicx,float,times}
%\usepackage{sectsty}
%\usepackage{authblk}
\usepackage{textcomp}
\usepackage{cite}
% \graphicspath{{../pdf/}{../jpeg/}}
% \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\usepackage[caption=false,font=footnotesize]{subfig}

\usepackage{url}

@@

\title{Title}

\author{\IEEEauthorblockN{Ching-Chun (Jim) Huang}
\IEEEauthorblockA{Department of Computer Science and\\Information Engineering\\
National Cheng Kung University, Taiwan\\
No.1, University Road, Tainan City 701, Taiwan (R.O.C.)\\
Email: jserv@ccns.ncku.edu.tw}
\and
\IEEEauthorblockN{Chung-Fan Yang}
\IEEEauthorblockA{Department of Electrical Engineering\\
National Cheng Kung University, Taiwan\\
No.1, University Road, Tainan City 701, Taiwan (R.O.C.)\\
Email: E24026048@mail.ncku.edu.tw}}

@@

@@

\section{Methodology}

    Based on the works presented above, we had found out several problems in common methodology method used currently.
    First, the methodology tool, e.g. cyclictest \cite{cyclictest} \cite{rt-tests}, is over-simplified. It only gives the wakeup latency
    measurements, which sometimes is not the main or only performance bottle-neck of a real-time system. Also, general
    profiling tools, e.g. perf \cite{perf}, is typically utilizing the sampling methodology method, lacking high
    fidelity, all-recorded profiling result of the target system in microsecond scale, which is usually seen in
    real-time system tuning. In addition, the behavior and loading characteristic of work-load used during test, e.g.
    hackbench, stress \cite{rt-tests}, etc. are far from the real target applications. These problems
    not only would significantly reduce the effectiveness of tuning target system, but also will cause actual hazards,
    harming the real-time performance, obscure.

    Our approach to counter these problems includes a new profiling method and a test work-load, which is able to
    represent the target real-time application. The new profiling tool is derived from paper A Decade of Wasted Cores,
    published during EuroSys 2016 \cite{Lozi:2016:LSD:2901318.2901326}. In A decade of Wasted Cores, authors have
    development a profiler which instruments the scheduler of Linux Kernel, extracting scheduling information. Based on
    this work we have extended the ability of the profiler to extract the running entity of each core of the target
    system also the context-switching information, including time and target process id (PID). This enabled us to record
    and collect kernel scheduling information, running PID of each processor core fully during the execution of
    work-load. The recorded data resolution is based on the timer resolution of kernel scheduler. On x86-64 and ARM
    platform, the resolution could achieve sub-microsecond level. This gives us the advantage to justify when would the
    processor core executes the real-time task, how work-loads were scheduled by the kernel scheduler, and random
    scheduling events. This level of detail could not be achieved with the previous mentioned tools, which only utilizes
    the processor's performance measurement unit (PMU), lacking the fidelity requires during the tuning of real-time
    system.

@@

\section{Experiment}

    In aid of these developed tools and work presented above, we proposed a high accuracy methodology system, and apply
    this on various platform, including x86-64 and ARM. The experiment platform is running Linux Kernel version 4.4 with
    PR\textunderscore RT \cite{preemptrt} patch and it's built with buildroot \cite{buildroot} package.

\subsection{Profiling Tool Evaluation}

    With the newly developed profiling tool, we were able to capture a specified task's execution period in microsecond
    level. To evaluate this we execute various work-load on the experiment platform, Altera Cyclone5 SoC development
    kit, hosting dual core ARM Cortex-A9 processor with 1Gb memory. First, a cyclistest executing solely is shown in
    figure 1. The area high lighted with gray are the real-time task being executed by cpu, with black bars marking the
    switching-in and switching-out point. Also, cooperating with the heat map of scheduler run-queue size shown in
    figure 2, we can tell that whether other tasks arrive in the scheduler together with real-time task with short
    inter-arrival time. In these circumstances, preemption and re-scheduling might occur. While testing how different
    loading conditions interference the real-time task, we observed that the jitter will increase when the number of
    tasks in system (real-time tasks and work-load tasks) increases. Diving into this problem, we modified the profiling
    tool to record the scheduling duration of real-time task. The result of profiling is in figure 3-a and 3-b, showing
    that in no-load and mild-load condition, the schedule duration are less than 10us, but with heavy-load condition,
    shown in figure 3-c, the schedule duration will ramp up to 30us in maximum. This hints us that although the CFS
    scheduler is able to determine which task to be switched-in in O(1) time \cite{cfs}, additional overhead exist. This overhead
    would increase alone with the system's loading condition.

\subsection{Comparison of Kernel and User-space Execution}

\subsubsection{Profiling System Call Overhead}

    With our work-load framework, we constructed a work-load called mctest, which resemble a real-time robot control
    system. This algorithm includes various computational heavy code and system-calls. Putting this work-load into
    execution on Freesacle i.mx6 Sabre platform which hosted 4 core ARM Cortex-A9 processor with 1Gb memory. We also
    enabled tickless feature \cite{tickless} of Linux kernel and isolate CPU 1 from scheduler use \cite{isolatedcpu}.
    Putting mctest on isolated and tickless CPU 1, we recorded the execution jitter. The result is shown in figure 4.
    With this result, we could suggest that the system call generates a large amount of jitter. And the overhead of
    system call will increase alone with the loading condition of the system. Figure 5 shows the execution jitter with
    load. As a result, rewriting real-time application as a kernel module is the only feasible approach.

\subsubsection{Kernel Mode Linux}

    While rewriting the real-time application in kernel module would reduce the execution jitter. This approach is
    difficult and tedious. Thus, it's not feasible to be wildly deployed. As the source of jitter, system call, has been
    identified. We applied an different approach, Kernel Mode Linux (KML) \cite{KML} \cite{KMLConf}. KML enables the
    ability for specified user-space program to access kernel address space directly. Thus, system calls become jump
    instructions, not instruction trapping the processor. In addition, we have also rewired system calls, which have
    vDSO implementations \cite{vDSO}, to use vDSO implementation via KML. This approach, executing in the same
    environment as above section, could reduce the user-space execution jitter comparable to kernel module approach,
    shown in figure 6. Therefore, KML have enable the ability to write real-time application user-space and exploit
    kernel-space performance to it.

\section{Conclusion}

    We have evaluated the real-time behavior of Linux by profiling kernel scheduler and measuring the latency of various
    kernel variants. An intensive interrupt load can cause long OS latencies due to the design of the interrupt
    processing mechanism. We proposed new tools to visualize task scheduling in fine-grained scale(microsecond level).
    This enabled us not only focusing on interrupt latency, but also scheduler durations, lock, and etc. It would thus
    be highly desirable to combine existing techniques, e.g KML, isolated CPU, tickless kernel, to improve task
    responsiveness under various target application characteristics, on top of PREEMPT\textunderscore RT.

\bibliographystyle{IEEEtran}
\bibliography{references}

\end{document}
